The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Changed how title appears in paper
Minor changes to intro of paper

\newenvironment{nouppercase}{%
\let\uppercase\relax%
\renewcommand{\uppercasenonmath}[1]{}}{}

@@

\begin{document}
\title{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}

@@

\begin{nouppercase}
\maketitle
\end{nouppercase}

@@

There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FrobeniusThresholds}.
\begin{itemize}
\item[$\circ$] \autoref{sec.Nu} describes the methods for approximating the $F$-pure threshold and other $F$-thresholds.  
\item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
\item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}. 
\end{itemize}
This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in prime characteristic commutative algebra.

\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FrobeniusThresholds} package.
Our package coauthors are Dan Smolkin (LIST MORE NAMES), and Zhibek Kadyrsizova, Moty Katzman (LIST MORE NAMES) contributed valuable code to the package. 
%Erin Bela, Juliette Bruce, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Matthew Mastroeni

@@

First, if {\tt ContainmentTest} is set to {\tt StandardPower}, then the ideal containments checked when computing {\tt nu(e,I,J)} are verified directly.
That is, a standard power of $I$ is first computed, say $I^n$, and a check is then run to see if the resulting ideal lies in the $p^e$-th Frobenius power of $J$.
Alternately, if {\tt ContainmentTest} is set to {\tt FrobeniusRoot}, then the ideal containments are verified through the computation of Frobenius roots.  That is, the $p^e$-th Frobenius root of $I^n$ is first computed, and a check is then run to see if it lies in $J$.  The output is unaffected, but this option often speeds up computations, especially when a polynomial or principal ideal is passed as the second argument.

>>>>

\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhead[RO, LE]{\thepage}
\fancyhead[C]{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}

\makeatletter
\def\@settitle{\begin{center}%
  \baselineskip14\p@\relax
    \bfseries
    \normalfont\LARGE%<- NEW
\@title
  \end{center}%
}
\makeatother

@@

\begin{document}
\title[]{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}

@@

\maketitle

@@

There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FrobeniusThresholds}.
\begin{itemize}
\item[$\circ$] \autoref{sec.Nu} describes the fundamental function {\tt nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ described above.  
\item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
\item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}. 
\end{itemize}
This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in prime characteristic commutative algebra.

\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FrobeniusThresholds} package.
Our package coauthors are Dan Smolkin {\color{red}(LIST MORE NAMES)}, and Zhibek Kadyrsizova, Moty Katzman {\color{red} (LIST MORE NAMES)} contributed valuable code to the package. 
%Erin Bela, Juliette Bruce, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Matthew Mastroeni

@@

First, if {\tt ContainmentTest} is set to {\tt StandardPower}, then the ideal containments checked when computing {\tt nu(e,I,J)} are verified directly.
That is, a standard power of $I$ is first computed, say $I^n$, and a check is then run to see if the resulting ideal lies in the $p^e$-th Frobenius power of $J$.

%{\color{red} \[ I \subseteq J^{[p^e]} \iff I \subseteq I^{[1/p^e]} \subseteq J.\]}

Alternately, if {\tt ContainmentTest} is set to {\tt FrobeniusRoot}, then the ideal containments are verified through the computation of Frobenius roots.  That is, the $p^e$-th Frobenius root of $I^n$ is first computed, and a check is then run to see if it lies in $J$.  The output is unaffected, but this option often speeds up computations, especially when a polynomial or principal ideal is passed as the second argument.
